### 2024-03-21 paper/main.tex
typo

Perhaps non-obviously, for a monomial to be in Deep Sets form, it must consist only of products of sums over the three points.
It cannot contain any differences, or any sums over pairs of points (or edges).
Thus $(\sum_{i=1}^2 x_i^2)\,(\sum_{i=1}^3 x_i\,y_i)$ is a permitted monomial, but nothing of the form $(\sum_{i=1}^3\sum_{j=1}^3 x_i^2\,y_j^2)$ is not permitted.
These monomials are both correct from a units perspective, but the second is not in Deep Sets form, because it contains products of position coordinates from different points.

>>>>

Perhaps non-obviously, for a monomial to be in Deep Sets form, it must consist only of products of sums over the three points.
It cannot contain any differences, or any sums over pairs of points (or edges).
Thus $(\sum_{i=1}^2 x_i^2)\,(\sum_{i=1}^3 x_i\,y_i)$ is a permitted monomial, but $(\sum_{i=1}^3\sum_{j=1}^3 x_i^2\,y_j^2)$ is not a permitted monomial.
These monomials are both correct from a units perspective, but the second is not in Deep Sets form, because it contains products of position coordinates from different points.
